---
title: "Homework 1"
author: "Maliat Islam"
date: "8/29/2021"
output:
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

library(animation)
```

### For this assignment, build the first letters for both your first and last name using point plots in R.  For example, the following code builds an H.

```{r creates an H}
par(mar=rep(4,4))
x=c(rep(0,500),seq(0,1,length.out=1000), rep(1,500))
y=c(seq(-1,1,length.out=500),rep(0,1000), seq(-1,1,length.out=500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))
```
### creating M

```{r creates a M}

x = c(rep(0, 1000), seq(0, 1, length.out = 700), seq(1, 2, length.out = 700), rep(2, 1000))

y = c(seq(-1, 1, length.out = 1000), seq(1, 0, length.out = 700), seq(0, 1, length.out = 700), seq(1, -1, length.out = 1000))

z = rbind(x, y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

```





### Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation , and 4) projection in animated fashion.  
```{r}
a=diag(2)
x11()
for (i in seq(-3,3, length.out=50)){
  a[1,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[-1,-1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
#Shearing horizontally
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[1,2]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
#Shearing vertically
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[2,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
```


## Creating I

```{r creates an I}
x=c(rep(1,500),seq(1,1,length.out=1000), rep(1,500))
y=c(seq(-1,1,length.out=500),rep(0,1000), seq(-1,1,length.out=500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

```
### Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation , and 4) projection in animated fashion. 

```{r}
a=diag(2)
x11()
for (i in seq(-3,3, length.out=50)){
  a[1,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[-1,-1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)
}
#Shearing horizontally
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[1,2]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
#Shearing vertically
a=diag(2)
for (i in seq(-3,3, length.out=50)){
  a[2,1]=i
  tran=apply(z,2,function(x) a%*%x)
  plot (tran[2,] ~ tran[1,], xlim=c(-3,3), ylim=c(-3,3))
  ani.record()
  #Sys.sleep(1)  
}
```




